---
title: "Marriage License Data"
author: 
  - Maria Mangru
thanks: "Code and data are available at: https://github.com/MariaMangru/Marriage-Licence."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(readr)

cleaned_data <- read_csv("../data/analysis_data/analysis_data.csv")

```

# Introduction

In this short paper we used @citeR, @opendatatorotno and @rohan.

The remainder of this paper is structured as follows. @sec-data provides a scatter plot of the marriage data. @sec-discussion contains the discussion.

# Data {#sec-data}

The figure (@fig-marriage) below shows the number of marriage licenses issued in Toronto between 2011 to 2024. We can see a fairly consistent pattern up to 2020, with fluctuations between 0 and approximately 1000 licenses per period.

However, post-2020, there appears to be an increase in the variation and frequency of licenses issued. This trend could be as a result of the COVID-19 pandemic in 2020 which may have caused delays or surges in marriage license applications.

```{r}
#| label: fig-marriage
#| fig-cap: Marriage
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv("../data/analysis_data/analysis_data.csv")

analysis_data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()
```

{{< pagebreak >}}


# Discussion {#sec-discussion}

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional data details

\newpage

# References
